---
title: "QA Defects Analysis - Preliminary Study"
author: "neocklee"
date: "January 31, 2016"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

Defect Analysis - Impact
========================================================

"An ounce of prevention is worth a pound of cure."

- The longer a defect stays in process, the more expensive it is to fix
- The cost of finding and fixing always one of the most expensive development activities
- Project risk increase if discovered issues at later stage

Defect Analysis - Early Discovery
========================================================

Why headmap?

- Volume of data increase and getting complex
- Compare performance on diffrent projects/phases using visual
- Distinguish level of urgency using color/visual
- Provide a quick glance prior in-depth analysis

This application will provide someone a high level overview of where we shall spend the effort in.
This is to prevent further damage to the projects. 

To learn more about the project, [Shiny Apps](https://neocklee.shinyapps.io/ProjectHeatMap/)



Defect Analysis using R
========================================================

googleVis being selected due to the support of interactive data driven analysis

- Parent level - Test Environments (Development or SIT)
- Size of the box - Defect count
- Grouping/Label in chart - Root cause of defects

Following sample code snippet
```{r, eval=FALSE, echo = TRUE}
gTreeMap <- gvisTreeMap(  myData,
idvar="Root.Cause", parentvar = "Environment",
sizevar = "Defect.Count", colorvar = "Defect.Log"))
```

Complete source code, [Github](https://github.com/neocklee/ShinyApp)


Defect Analysis Sample Output
========================================================
* The sample output is currently support single tier
    + It can be enhanced in the future stage to support multi tiers

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(googleVis)
library(lubridate)
library(dplyr)

data <- read.csv("http://raw.githubusercontent.com/neocklee/ShinyApp/master/data/QASReport.csv",stringsAsFactors=FALSE)
myEnv <- 'Test/SIT'
startDate <- "2016-01-01"
endDate <- "2016-01-31"
# data filteration
myData <- data[ data$Environment==myEnv,]
# Data processing
myData$Detected.on.Date <- as.Date(myData$Detected.on.Date, format = "%d/%m/%Y")
myData <- myData[myData$Detected.on.Date >= startDate & myData$Detected.on.Date <= endDate, ]
myData[ myData$Root.Cause =='',]$Root.Cause <- 'New Defects'
myDataFinal <- myData %>%
  group_by(Environment, Root.Cause) %>%
    select(Defect.ID, Root.Cause, Environment) %>%
       summarise( Defect.Count =length( Defect.ID) )
## Create parent variable
total=data.frame( Defect.Count=sum(myDataFinal$Defect.Count), Environment=NA, Root.Cause=myEnv)
myDataFinal <- rbind(myDataFinal,total)
myDataFinal$Defect.Log = log(myDataFinal$Defect.Count)
gTreeMap <- gvisTreeMap(  myDataFinal,
              idvar="Root.Cause", parentvar = "Environment",
              sizevar = "Defect.Count", colorvar = "Defect.Log",
              options=list(width=600, height=500,
                           fontSize=16,
                           minColor='#EDF8FB',
                           midColor='#66C2A4',
                           maxColor='#006D2C',
                           headerHeight=20,
                           fontColor='black',
                           showScale=TRUE,
                           useWeightedAverageForAggregation =TRUE))

```

```{r opts.label = 'interactive', results = 'asis', echo=TRUE}
print(gTreeMap, tag = 'chart')
```
